Tight Generalization Bounds for Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-10-12 arxiv/conclusions.tex
sec 6

We describe several open questions for future work.
First, our bound in Corollary \eqref{cor_MTL_loss} involves an error term that scales down with $n_1$.
Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two random matrices $Z^{(1)}, Z^{(2)}$ with isotropic covariances.
This might require new techniques beyond \HZ{to add}.
Second, it would be interesting to extend our results to classification problems.
Several recent work have made remarkable progress in the (one-sample) high-dimensional logistic regression setting \cite{sur2019modern}.
An interesting question is to study hard parameter sharing in (multiple-sample) high-dimensional logistitic regression.

>>>>

We describe several open questions for future work.
First, our bound in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two random matrices $Z^{(1)}, Z^{(2)}$ with isotropic covariances.
This requires studying the asymptotic distribution of the singular values of $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)} + 1$, which is still an open problem in random matrix theory. We remark that the eigenvalues distribution of this matrix have been studied in the name of Fisher matrices \cite{Fmatrix}, but its singular values will follow a different distribution since the matrix is not symmetric.
 %might require new techniques beyond the current ones in random matrix theory .%\HZ{to add}.
Second, it would be interesting to extend our results to classification problems.
Several recent work have made remarkable progress in the (one-sample) high-dimensional logistic regression setting \cite{sur2019modern}.
An interesting question is to study hard parameter sharing in (multiple-sample) high-dimensional logistitic regression.
